\papertitle

### 2017-10-13 article-icmc2017.tex
minor

\capstartfalse
\maketitle
\capstarttrue
\begin{abstract}
    Numeric musical and artistic creation is in great part based on well-known patcher softwares: Max/MSP, PureData, OpenMusic, vvvv\dots

@@

A method for dynamic patching of Max abstractions based on CommmonLisp has been proposed by Thomas Hummel\cite{hummel1994common} to reduce resource usage by enabling and disabling sub-patches at different points in the execution of a program.
This has the advantage of saving computing power for the active elements of the score.

@@

During a tick, ports have access to three sets of values, corresponding to scopes: 
\begin{itemize}
  \item {Global scope: The values that were in the environment at the beginning of the tick. 
  These values are accessible to every process.}
  \item {Local scope: The values produced by previous implicit output ports in the dataflow.
        Section~\ref{sec.relationships} presents the various policies that nodes can leverage to use these values. 
        The local scope is cleared at the beginning of a tick. 
        The values written to it are committed to the global environment at the end of the tick.}
  \item{Connection scope: the explicit scope between two ports; the data flowing from one out port can only go to input ports it is connected to. This is the explicit case.}
\end{itemize}

>>>>

\capstartfalse
\maketitle
\capstarttrue
\begin{abstract}
    Numeric musical and artistic creation is in great part based on well-known patcher softwares: Max, PureData, OpenMusic, vvvv\dots

@@

A method for dynamic patching of Max abstractions based on CommonLisp has been proposed by Thomas Hummel\cite{hummel1994common} to reduce resource usage by enabling and disabling sub-patches at different points in the execution of a program.
This has the advantage of saving computing power for the active elements of the score.

@@

During a tick, ports have access to three sets of values, corresponding to scopes: 
\begin{itemize}
  \item {Global scope: The values that were in the environment at the beginning of the tick. 
  These values are accessible to every process.}
  \item {Local scope: The values produced by previous implicit output ports in the dataflow.
        Section~\ref{sec.relationships} presents the various policies that nodes can leverage to use these values. 
        The local scope is cleared at the beginning of a tick. 
        The values written to it are committed to the global environment at the end of the tick.}
  \item{Connection scope: the explicit scope between two ports; the data flowing from one output port can only go to input ports it is connected to. This is the explicit case.}
\end{itemize}
